Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
more copyediting

\langName, like \origLang, includes angle bracketed expressions which represent
values or expressions which could differ between two runs of the program.  As we
will see when discussing the type system, this corresponds to values and
expressions that have high security labels on their types.

>>>>

\langName, like \origLang, includes angle bracketed expressions which represent
values and expressions which could differ between two runs of the program.  As we
will see when discussing the type system, this corresponds to values and
expressions that have high security labels on their types.
